Classifying Patent Based on their Semantic Content \\ An empirical exploration into patent text mining

### 2018-12-13 Docs/Papers/Technical/Slides_giessen.tex
slides_cfe

In practice, patent data are available in the form of a relational database.
\end{frame}
\begin{frame}{Motivation}
    \begin{figure}
        \centering
        \includegraphics[width=0.8\linewidth]{figures/patent_abstract_ex.png}
        \caption{Example of patent front page. Source : USPTO}
    \end{figure}
\end{frame}
\begin{frame}{Patents and text-mining}
    \begin{itemize}
        \item Main usage: matching between patents and firms/inventors
        \item Used in the search of prior-art/litigation
        \item Technology mapping
    \end{itemize}
\end{frame}
\begin{frame}{Why study patents ?}
%\justify

@@

\end{frame}
\section{Background}

@@

>>>>

In practice, patent data are available in the form of a relational database.
\end{frame}
\begin{frame}{Motivation}
    \begin{figure}
        \centering
        \includegraphics[width=0.8\linewidth]{figures/patent_abstract_ex.png}
        \caption{Example of patent front page. Source : USPTO}
    \end{figure}
\end{frame}

\begin{frame}{Patents and text-mining}
    \begin{itemize}
        \item Main usage: matching between patents and firms/inventors
        \item Used in the search of prior-art/litigation
        \item Technology mapping
    \end{itemize}
\end{frame}
\begin{frame}{Why study patents ?}
%\justify

@@

\begin{frame}{An example of classification outcome}
    \begin{center}
	\includegraphics[width=0.8\textwidth]{figures/6833896.png}
	\end{center}

	\medskip
	\hrule

	\textbf{Technological classes:} 349 (Liquid Crystal Cells, Elements and Systems), 257 (electrodes)

	\textbf{Prior art keywords (Google Patents):} layer, method, gate, electrode, substrate

	\textbf{Most central keywords (our method):} substrat, semiconductor, insul, gate, transistor

\section{Background}

@@

\textbf{Paper: } Bergeaud, A., Potiron, Y., & Raimbault, J. (2017). Classifying patents based on their semantic content. PloS one, 12(4), e0176310.

### 2018-12-13 Docs/Papers/Technical/overleafv2/Slides.tex
slides_cfe

\title[Patent Mining]{Classifying Patent Based on their Semantic Content \\ An empirical exploration into patent text mining}
\author[Bergeaud, Potiron, Raimbault]{Antonin Bergeaud \and Yoann Potiron \and Juste Raimbault}
\institute[]{Banque de France, Keio University and ISC-PIF}
\date{November 2018}

@@

\section{Introduction}
\begin{frame}{Motivation}
    %Patenting is increasing, big data blablabla

    \textit{Patenting as a footprint of technology and its coevolution with science and culture~\cite{bais2010praise}}

\bigskip
\centering

\includegraphics[width=0.35\textwidth,angle=90]{figures/USX1}
\includegraphics[width=0.45\textwidth]{figures/pageRank}

\end{frame}
\begin{frame}{Motivation}
    \begin{figure}
        \includegraphics[width=0.8\linewidth]{figures/patent_usa.png}
        \caption{Log number of patent applications per capita at the USPTO. Source : USPTO}
    \end{figure}
\end{frame}
\begin{frame}{Motivation}
What are patents?
\begin{itemize}
    \item Property rights to an invention (novelty, non-obviousness and industrial applicability). Set the state of the art of a technology.
    \item Classification system in technology fields (or classes).
    \item Concept of ``Person having ordinary skill in the art'': an invention must be sufficiently disclosed in the description of the patent.
    \item Different realities between countries/IP offices (USPTO, EPO, JPO, CNIPA...).
\end{itemize}

In practice, patent data are available in the form of a relational database.
\end{frame}
\begin{frame}{Motivation}
    \begin{figure}
        \centering
        \includegraphics[width=0.8\linewidth]{figures/patent_abstract_ex.png}
        \caption{Example of patent front page. Source : USPTO}
    \end{figure}
\end{frame}
\begin{frame}{Patents and text-mining}
    \begin{itemize}
        \item Main usage: matching between patents and firms/inventors
        \item Used in the search of prior-art/litigation
        \item Technology mapping
    \end{itemize}
\end{frame}
\begin{frame}{Why study patents ?}
%\justify

$\rightarrow$ Although imperfect, patents are the most commonly used measure of innovation in economics. \\ % return to innovation, matching with firms, citation analysis...
$\rightarrow$ Applied Epistemology : particular case of the ecology and evolution of knowledge; diffusion of knowledge.
\bigskip

\textbf{Examples :}

@@

\end{frame}
\section{Background}

@@

\begin{itemize}
\item Parsing and tokenizing / pos-tagging (word functions) / stemming  with \texttt{nltk}
\item Selection of potential \textit{n-grams} (with $1 \leq n \leq 3$) with the rule $\bigcap \{NN \cup VBG \cup JJ \}$
\item Database insertion for instantaneous use (several days $\rightarrow$ 1min)
\item Estimation of \textit{n-grams} relevance, following co-occurrences statistical distribution (\textit{termhood} score as chi-2 score)
\end{itemize}
\end{frame}

@@

    \hyperlink{slide:sensitivity}{\beamerbutton{Sensitivity analysis}}

@@

%\justify

@@

\section{Conclusion}
\begin{frame}{Possible developments}
\textbf{Direct}
    \begin{itemize}
        \item Look at the correlation between patent quality indicators and centrality indices.
        \item Use patent-firm matching to study a \emph{firm-level} semantic network.
        \item Extending the analysis to other patent offices (EPO/JPO).
    \end{itemize}
    \pause
\textbf{Economic}
    \begin{itemize}
        \item Linking semantic measures to values of firms
        \item Can semantic proximity helps understand M\&A?
        \item Firms trajectories in relation to their life-cycle
    \end{itemize}
    \pause
\textbf{Technology}
\begin{itemize}
    \item Measure of complementarity between technology?
    \item Possible application to detection of emerging research fronts
    \item An interactive exploration of semantic content?
\end{itemize}
\end{frame}

\begin{frame}{Other projects}
    %\justify

@@

\bigskip
\bigskip

\textbf{Open repository} at \texttt{https://github.com/JusteRaimbault/PatentsMining}\\\medskip
\textbf{Raw database} at \texttt{http://dx.doi.org/10.7910/DVN/BW3ACK}\\\medskip 
\textbf{Semantic classification database} at  \texttt{http:// dx.doi.org/10.7910/DVN/ZULMOY}\\\medskip
\textbf{Acknowledgments}: thanks to ISC-PIF for access to the computation infrastructure.

@@

@@

    Directed simple modularity \cite{nicosia2009extending}
    \[
Q_d^{(z)} = \displaystyle \frac{1}{N_P}\sum_{1\leq i,j\leq N_P}\left[A_{ij} - \frac{k_{i}^{in}k_{j}^{out}}{N_P}\right]\delta(c_i,c_j),
\]

>>>>

\title[Patent Mining]{Classifying Patent Based on their Semantic Content \\ An empirical exploration into patent text mining}
\author[Bergeaud, Potiron, Raimbault]{Antonin Bergeaud \and Yoann Potiron \and Juste Raimbault}
\institute[]{Banque de France, Keio University and ISC-PIF}
\date[14/12/2018]{Computational and Financial Econometrics\\
Session Text Mining\\
14 December 2018}

@@

\section{Introduction}

%\begin{frame}{Motivation}
%    %Patenting is increasing, big data blablabla
%    
%    \textit{Patenting as a footprint of technology and its coevolution with science and culture~\cite{bais2010praise}}
%
%\bigskip
%\centering
%
%\includegraphics[width=0.35\textwidth,angle=90]{figures/USX1}
%\includegraphics[width=0.45\textwidth]{figures/pageRank}
%    
%\end{frame}
\begin{frame}{Motivation}
    \begin{figure}
        \includegraphics[width=0.8\linewidth]{figures/patent_usa.png}
        \caption{Log number of patent applications per capita at the USPTO. Source : USPTO}
    \end{figure}
\end{frame}
\begin{frame}{Motivation}
What are patents?
\begin{itemize}
    \item Property rights to an invention (novelty, non-obviousness and industrial applicability). Set the state of the art of a technology.
    \item Classification system in technology fields (or classes).
    \item Concept of ``Person having ordinary skill in the art'': an invention must be sufficiently disclosed in the description of the patent.
    \item Different realities between countries/IP offices (USPTO, EPO, JPO, CNIPA...).
\end{itemize}

In practice, patent data are available in the form of a relational database.
\end{frame}
\begin{frame}{Motivation}
    \begin{figure}
        \centering
        \includegraphics[width=0.8\linewidth]{figures/patent_abstract_ex.png}
        \caption{Example of patent front page. Source : USPTO}
    \end{figure}
\end{frame}
\begin{frame}{Why study patents ?}

$\rightarrow$ Although imperfect, patents are the most commonly used measure of innovation in economics. \\ % return to innovation, matching with firms, citation analysis...
$\rightarrow$ Applied Epistemology : particular case of the ecology and evolution of knowledge; diffusion of knowledge.

\textbf{Patents and text-mining: }

    \begin{itemize}
        \item Main usage: matching between patents and firms/inventors
        \item Used in the search of prior-art/litigation
        \item Technology mapping
    \end{itemize}
\end{frame}

%\begin{frame}{Why study patents ?}
%\textbf{\textcolor{red}{virer ?}}
%\justify
%
%$\rightarrow$ Although imperfect, patents are the most commonly used measure of innovation in economics. \\ % return to innovation, matching with firms, citation analysis...
%$\rightarrow$ Applied Epistemology : particular case of the ecology and evolution of knowledge; diffusion of knowledge.
%\bigskip

%\textbf{Examples :}

%\begin{itemize}
%\item \cite{griliches1998patent}: patent as an economic indicator
%\item \cite{Youn:2015fk} interaction between technological fields ; combinatorial nature of inventions
%\item \cite{2016arXiv160207928B} citation network analysis to detect emerging research front
%\item \cite{gerken2012new} \cite{tseng2007text} semantic analysis (remains limited to specific fields and time windows)
%\end{itemize} 
%\end{frame}

@@

\begin{frame}{An example of classification outcome}
    \begin{center}
	\includegraphics[width=0.8\textwidth]{figures/6833896.png}
	\end{center}

	\medskip
	\hrule

	\textbf{Technological classes:} 349 (Liquid Crystal Cells, Elements and Systems), 257 (	Active solid-state devices)

	\textbf{Prior art keywords (Google Patents):} layer, method, gate, electrode, substrate

	\textbf{Most central keywords (our method):} substrat, semiconductor, insul, gate, transistor

\section{Background}

@@

\begin{itemize}
\item Parsing and tokenizing / pos-tagging (word functions) / stemming  with \texttt{nltk}
\item Selection of potential \textit{n-grams} (with $1 \leq n \leq 3$) with the rule $\bigcap \{NN \cup VBG \cup JJ \}$
%\item Database insertion for instantaneous use (several days $\rightarrow$ 1min)
\item Estimation of \textit{n-grams} relevance, following co-occurrences statistical distribution (\textit{termhood} score as chi-2 score), filtering on relevance to construct co-occurence network
\item Filtering of network edge (parameter $\theta_w$), with an additional exogenous control by technological class keyword concentration to filter nodes (parameter $\theta_c$)
\end{itemize}
\end{frame}

@@

@@

@@

\section{Conclusion}
\begin{frame}{Possible developments}
\textbf{Direct}
    \begin{itemize}
        \item Look at the correlation between patent quality indicators and centrality indices.
        \item Use patent-firm matching to study a \emph{firm-level} semantic network.
        \item Extending the analysis to other patent offices (EPO/JPO).
    \end{itemize}
    \pause
\textbf{Economic}
    \begin{itemize}
        \item Linking semantic measures to values of firms
        \item Can semantic proximity helps understand M\&A?
        \item Firms trajectories in relation to their life-cycle
    \end{itemize}
    \pause
\textbf{Technology}
\begin{itemize}
    \item Measure of complementarity between technology?
    \item Possible application to detection of emerging research fronts
    \item An interactive exploration of semantic content?
\end{itemize}
\end{frame}
\begin{frame}{Other projects}

@@

%\bigskip

\textbf{Paper: } Bergeaud, A., Potiron, Y., \& Raimbault, J. (2017). Classifying patents based on their semantic content. PloS one, 12(4), e0176310.

\medskip
\textbf{Open repository} at \texttt{https://github.com/JusteRaimbault/PatentsMining}\\\medskip
\textbf{Raw database} at \texttt{http://dx.doi.org/10.7910/DVN/BW3ACK}\\\medskip 
\textbf{Semantic classification database} at  \texttt{http:// dx.doi.org/10.7910/DVN/ZULMOY}\\\medskip
\textbf{Acknowledgments}: thanks to ISC-PIF for access to the computation infrastructure.

@@

\begin{frame}{Previous work on patents and text-mining}

@@

    Directed simple modularity:
    \[
Q_d^{(z)} = \displaystyle \frac{1}{N_P}\sum_{1\leq i,j\leq N_P}\left[A_{ij} - \frac{k_{i}^{in}k_{j}^{out}}{N_P}\right]\delta(c_i,c_j),
\]
